\begin{document}
While humans effortlessly recognize shapes and objects through our complex visual cortex system where we have millions of neurons and
billions of connections between between these and were fine tuned through generations. The difficulty of visual pattern detection becomes
apparent when trying to implemented the logic in an algorithm.\cite{neuralnetworksanddeeplearning} 
\newline
\newline
Object Detection which is a technology related to computer vision or image processing is a field that deals with the recognition of objects in a digital image or video.
\newline
While Machine Learning is a subset of Artificial Intelligence where the computer will perform tasks through algorithms and models without explicit instructions, relying on patterns  and models instead.
\newline
\newline
Combining these two technologies and the recent advances in Object Detection through region proposal methods and region-based convolutional
neural networks opened up new possibilities which were impossible to achieve before through low level feature analysis only such as mean color comparison, shape and filter analysis or other methods which were common before.
\newline
\newline
Region proposal methods typically rely on inexpensive features and economical inference schemes. Selective Search, one of the most popular
methods, greedily merges superpixels based on engineered low-level features. Yet when comparing to efficient detection networks, Selective
Search takes 2 seconds per Image on a CPU implementation, whereas fast region-based CNN's take advantage of the GPU and therefore are not applicable for comparison.\cite{fasterrcnn}
\newline
\end{document}
